\TITLE

### 2023-01-30 paper/content.tex
split the tex into subtexs

\documentclass{ieeeaccess}

\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}

\usepackage{caption}
\usepackage{url}
\usepackage{listings}
\usepackage{pdfpages}
\usepackage[english]{babel}
\usepackage{xcolor,colortbl}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\usepackage{scalerel}

\newcommand{\plus}{+}
\newcommand{\minus}{-}
\newcommand\neutral[1][.75]{\mathbin{\ThisStyle{\vcenter{\hbox{%
  \scalebox{#1}{$\SavedStyle\bullet$}}}}}%
}

\newcommand{\customer}{customer}
\renewcommand{\sp}{SP}

\newcommand{\normal}{n}
\newcommand{\dispute}{d}
\newcommand{\abnormal}{\overline{n}}
\newcommand{\abdispute}{\overline{d}}

\newcommand{\PoD}{$\mathrm{PoD}$}
\newcommand{\PoP}{$\mathrm{PoP}$}
\newcommand{\cid}{$\mathrm{cid}$}

\newcommand{\floor}[1]{\left\lfloor #1 \right\rfloor}
\newcommand{\ceil}[1]{\left\lceil #1 \right\rceil}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\history{Date of publication xxxx 00, 0000, date of current version xxxx 00, 0000.}
\doi{10.1109/ACCESS.2022.0122113}

\title{Privacy-preserving physical delivery service provisioning using distributed networks}
\author{\uppercase{Stanis\l{}aw Bara{\'n}ski} \authorrefmark{1},
\uppercase{Julian Szyma{\'n}ski\authorrefmark{1} } 
 }

\address[1]{Department of Electronic, Telecommunication and Informatics, Gdansk University of Technology, Narutowicza 11/12 Gdansk Poland (e-mail: stanislaw.baranski@pg.edu.pl, julian.szymanski@eti.pg.edu.pl}

\tfootnote{The work has been supported partially by the founds of Department of Computer Architecture Faculty of Electronics, Telecommunications and Informatics, Gdańsk University of Technology.}

\markboth{S. Bara{\'n}ski, J. Szyma{\'n}ski : 
Privacy-preserving physical delivery service provisioning using distributed networks}
{S. Bara{\'n}ski, J. Szyma{\'n}ski : 
Privacy-preserving physical delivery service provisioning using distributed networks}

\corresp{Corresponding author: Stanislaw Baranski (e-mail: stanislaw.baranski@pg.edu.pl).}

\begin{abstract}
Service providers like lawyers, laboratories, auditors, or banks, to provide services, require customers to submit data often associated with their personal information, exposing their customers to privacy risks. However, most service providers use personal information merely for logistic operations like payments and communication and could provide services anonymously if other means of logistics exist.
We propose a anonymous fair exchange protocol for coordinating service provision using blockchain for both anonymous payments and proofs of existence and content-addressable network for results delivery.
% Less important
A service provider can employ our protocol to provide services without collecting personal information, enabling services currently based on unacceptable trust assumptions. 
% Even less important
Possible applications for this protocol include anonymous tests for drugs, venereal diseases, paternity, and steroids, or anonymous legal advice.
We provide the fairness analysis and well as the implementation of the protocol. We discuss further extensions to an anonymous delivery system, and a decentralized conflict resolution system.
\end{abstract}

\begin{keywords}
Anonymity, blockchain, fair-exchange, physical delivery, privacy, services
\end{keywords}

\titlepgskip=-21pt

\maketitle

@@

Providing personal information exposes users to privacy risks, i.e. potential loss of control over personal information~\cite{smithInformationPrivacyResearch2011}.

Such personal information can be used deliberately or unintentionally
(e.g., by theft) for insider disclosure, unauthorized access, or commercial gains. For example, by reselling it to marketers, financial institutions, other businesses, government agencies, or even cybercriminals. Which in turn can lead to profiled advertisements or criminal activities like identity theft or illegal tracking and surveillance~\cite{smithInformationPrivacyResearch2011}.

Important individuals like influencers, politicians, or celebrities are especially vulnerable to this kind of attack as exposure of their health records, purchase habits, or legal documents can threaten their reputation, position or be used for blackmailing.

The privacy guarantee of the personal information is often based merely on trust assumptions and the security of the IT system. However, most SPs do not need personal information for any other reason than payment or communication, which should be considered secondary compared to actual service provision.

It would be desirable for the user to keep its identity private while still receiving the service. This could lead to reduced trust that users have to put on SPs and less responsibility borne by SPs.

Examples of services that would benefit from the anonymity property are:
\begin{itemize}
    \item Patients willing to take a test for drugs, venereal diseases, paternity or steroids have a strong incentive to keep the whole procedure private. Merely the fact that they took the test—without exposing the result—is suggestive enough to act as a premise in case of a conflict.

Especially celebrities, politicians, and public figures are prone to this kind of problem as such precedent can negatively influence their future career.

Currently, they have to risk that their personal details, materials, and results are stored securely and kept in private from any unauthorized actor (both curious employee and malicious attacker).

Our protocol allows taking such tests anonymously, eliminating the strong trust assumption put on the laboratories and their IT
systems.
\item People willing to take risky business activities may be willing to receive the risk estimation and prediction of possible personal repercussions of such action.

By exposing our identity we trust that the lawer will not use that information for harmful actions.

@@

@@

% Therefore we propose
We propose a protocol for anonymously provisioning services that require the delivery of physical materials. A service provider employing our protocol can provide services without collecting any personal information from customers.

In case of dispute, either due to exceeding deadlines or providing an incorrect result, the customer can disclose the whole interaction and prove to justice the misbehaviour of the SP.

To achieve these objectives, we use:
\begin{itemize}
    \item Blockchain (aka message board), to achieve fairness, i.e., as a means for proving that certain actions took place at a certain moment without the trusted third party (TTP).
    \item Anonymous payment methods, like cash or privacy-preserving cryptocurrencies, allowing customers to pay for the services anonymously.
    \item Content-addressable decentralised storage network (e.g., IPFS) to anonymously provide results to customers together with provable storage netwrok (e.g., Filecoin) to guarantee that the results are available to the customer even in case of the SP deny of service. 
    \item Cryptography
    \begin{itemize}
        \item Symmetric encryption, to encrypt and decrypt results published on the public networks.
        \item Public-key cryptography, and Diffie-Helman key exchange (DHKE) to derive shared secrets for symmetric encryption.
        \item Digital signatures, to achieve authentication and non-repudiation of actions. 
    \end{itemize}

@@

%\paragraph{Contributions}
We contribute to the state of the art by:

\begin{itemize}
\item proposing a novel protocol that:
  \begin{itemize}
  \item allows \textbf{anonymous} service provision, i.e., the service provider does not need to collect any personal information from the customer.
  \item achieves \textbf{fairness} by carefully designing the protocol as an interactive non-cooperative game, in which the SP remains in advantageous position, and customer in disadvantageus with the option to start a dispute in case the SP misbehaviour.
  \item \textbf{does not rely on centralized TTP}, but uses decentralized blockchain and distributed content-addressable storage network.
  \item abstracts the customers from the blockchain technology used underneath, allowing the use of our protocol for \textbf{non-technical users}.
  \item allows the \textbf{delivery of physical materials}, which was rarely addressed by other researchers or based on strong and unpractical assumptions.
  \item guarantees the \textbf{remote availability of the results}, even in case of the SP denial of service.
  \end{itemize} 
\item Systemise often misused definitions of anonymity, pseudonymity, linkability, and traceability.
\item Proposing a framework for analysing fairness analysis in fair-exchange protocols.
\item Discuss the possible improvements to the protocol witht the use of secure computation, self-sovereign identities, zero-knowledge proofs, and blockchain-based dispute resolution mechanisms.
\end{itemize}

@@

%\paragraph{Organisation}
The remainder of this paper is organized as follows.
In section~\ref{sec:related-works} we review related works. 
Then, in section~\ref{sec:building-blocks} we discuss the building blocks of dispute resolution system, blockchain as a message board, fairness, payment for services, storage network, result availability, anonymity and confidentiality.
Section~\ref{sec:protocol} describes how the protocol works in detail.
Section~\ref{sec:fairness-analysis} provides a fairness analysis of the proposed protocol.
In Section~\ref{sec:experiments} we present the implementation of the protocol and results of our experiments.
Section~\ref{sec:discussion} discuss possible improvements in terms of crowd sourced dispute resolution or dispute avoidance, self-sovereign identities (SSI), and anonymous delivery.
Finally, section~\ref{sec:conclusion} concludes the paper.

\section{Related Works}\label{sec:related-works}
In this section we review related works on fair exchange, anonymous, and physical delivery protocols. Then we outline the main differences between our protocol and the existing ones.

@@

The most common application of anonymous fair exchange protocols is e-commerce. The problem is that the customer wants to buy a product from a merchant, but does not want to reveal his identity to the merchant. The problem gets even more challenging when physical products are involved.

Authors of~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} proposed a protocol for fair exchange of physical products and electronic payments, which guarantee both customer and merchant anonymity. They achieve it by introducing online TTPs that validate coins and provide fair exchange guarantees.

The anonymity is ensured by assuming the existence of a source cabinet (SC), delivery cabinet (DC), and a trusted delivery agent who take a product from a SC and provide it to a DC.
Both cabinets provide access to the product by passwords to conceal
the identity of the customer and the merchant.

@@

\begin{enumerate}
    \item Both parties agree on the purchase details.
    \item The customer buys a digital coin from his bank and validates it with the TTP.
    \item The customer sends the merchant the purchase order and the digital signature made by TTP on the encrypted coin.
    \item The merchant post the product to the SC.
    \item Delivery agent collects the product from the SC and posts it to the DC.
    \item Customer collects the product from the DC using a password.
    \item The customer checks if the product is the ordered one.
    \begin{itemize}
    \item[-] if yes 
        \begin{enumerate}
        \setcounter{enumii}{7}
        \item the customer sends the acknowledge to the DC and decryption key to the merchant.
        \item The merchant redeem the coins from the bank.
        \end{enumerate}
    \item[-] if no
        \begin{enumerate}
        \setcounter{enumii}{7}
        \item the DC is equipped with a video camera that records the moment when the customer opens the package and lets the customer signal the invalidity of the product, and so, sending the encrypted recording to the TTP. 
        \item the dispute is settled via TTP, optionally letting each party reveal its identity.
    \end{enumerate}
    \end{itemize}
\end{enumerate}
\endgroup

However, the protocol relies on strong assumptions, namely:

\begin{itemize}
    \item there exists trusted third party (TTP) and trusted delivery agent which do not misbehave or collude with any party;
    \item there exists an anonymous communication channel 
    \item the customer's and merchant's banks enable confidential transactions, and both share commit-buffer where the value is locked until the transaction is finished;
    \item all banks maintain a global list of coins' serial numbers to prevent double-spending problems;
    \item the SC and DC exist, and in both, the access is protected by a password;
    \item the DC is equipped with a video camera that records the moment when the customer opens the package and provides a way to submit the video to TTP in case of a dispute;
\end{itemize}

@@

The issue of TTPs in fair exchange protocols has been solved by the usage of decentralised networks, especially blockchain technology.

The simplest example of blockchain-based fair exchange protocol is certified electronic mail protocol in which neither the sender can deny sending the mail, nor the receiver can deny receiving it. As the service is widely used in the paper world, achieving it for e-mails has not yet met the agreement across the scientific community. The main problem was the dependency of TTP, which significantly reduced the performance, security, and robustness of such protocols. The protocols that do not use TTP struggle with high computation and communication overhead~\cite{hinarejosSolutionSecureCertified2019}.

@@

The idea behind certified e-mails and any other fair exchange protocols is following:
\begin{enumerate}
    \item The sender sends encrypted and signed message to the receiver.
    \item The receiver returns a proof of delivery (a signature) of the encrypted message to the sender.
    \item The sender publishes proof of delivery and the decryption key on a blockchain (or TTP in general).
    \item The receiver decrypts the encrypted message using the published decryption key.
\end{enumerate}

@@

Next, both Alice and Bob, take their key shares, and encrypt each
\textit{i}-th key share using public key of \textit{i}-th mediator. As a result
Alice's secret \(x_A\) becomes \({c^A_1, c^A_2,...,c^A_n}\), and Bob's
secret \(x_B\) becomes \({c^B_1, c^B_2,...,c^B_n}\), where
\(c_i = E_{M_i}(P_i)\) is the encrypted \(i\)-th key share using
\(i\)-th mediator public key \(M_i\).

@@

In case of dispute, the decentralized network of mediators settle the conflict and grand one winning party, the other party secret key,
letting him withdraw the funds.

@@

Onchain smart-contract is used to coordinate the whole process and
mediate communication between customers and delivery providers.

@@

Bîrjoveanu, 2015~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} is the closest to our protocol, however it uses TTP and does not consider dispute between parties.

Hinarejos et al., 2019~\cite{hinarejosSolutionSecureCertified2019} is the simplest protocol that replaces TTP with blockchain. However, it does not consider anonymity, dispute between parties nor physical material exchange.

Meng et al., 2019~\cite{mengThemisDecentralizedEscrow2019} improves the previous protocol by the crownsource dispute resolution system. However it does not take anonimity into consideration.

Altawy et al., 2017~\cite{altawyLelantosBlockchainBasedAnonymous2017} is a blockchain-based protocol that does not provide dispute resolution, but provides anonymous physical delivery by using onion routing and anonymous blockchain interaction assuming unlinkability between pseudonyms and real identities.

Our protocol achieves stronger anonymity guarantees. Namely, we achieve anonimity by using either cash or privacy-preserving blockchains. Moreover, our protocol does not require a customer to submit any transaction to the message board, which may be the weakest link in the anonymity of aforementioned protocols.

Our protocol does not use its own delivery system. We assume that there is a way to anonymously deliver a package either via SP's drop box, or trusted party.

Also, our protocol does not provide its own dispute resolution mechanism as Themis does. However, we assume the existence of an abstract justice that accepts evidence and punishes the misbehaving party. It can be instantiated with either local court or police, or one of the blockchain
dispute resolution services like Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros~\cite{bergollaKlerosSociolegalCase2022,gudkovCrowdArbitrationBlockchain2020}, Aragon Court\footnote{Aragon Court, Decentralized Dispute Resolution Protocol, https://aragon.org/aragon-court, (last visited Jan. 10, 2023)}, LTO Network\footnote{LTO Network, 2019, https://lto.network/, (last visited Jan. 17, 2023)}, and other Online Dispute Resolution platforms~\cite{allenGovernanceBlockchainDispute2019}.

The comparision of the protocols is presented in table~\ref{tab:comparision}.

\begin{table}
  \newcommand{\YES}{\cellcolor{green!50}Yes}
  \newcommand{\ID}{\cellcolor{green!25}Identity}
  \newcommand{\PSEUDO}{\cellcolor{green!25}Pseudonym}
  \newcommand{\ANON}{\cellcolor{green!50}Anonymity}
  \newcommand{\NO}{\cellcolor{red!50}No}
  \newcommand{\TTP}{\cellcolor{red!50}TTP}
  \newcommand{\BC}{\cellcolor{green!50}BC}
  \caption{Related work comparision}
  \label{tab:comparision}
  \setlength{\tabcolsep}{3pt}
  \begin{tabular}{|p{40pt}|p{35pt}|p{40pt}|p{35pt}|p{30pt}|p{30pt}|}
  \hline
  Protocol & Fair exchange & Anonymity & Dispute resolution & Trust & Physical delivery \\
  \hline
  Bîrjoveanu, 2015~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} & \YES & \YES & \NO & \TTP & \YES \\
  \hline
  Hinarejos et al., 2019~\cite{hinarejosSolutionSecureCertified2019} & \YES & \NO & \NO & \BC & \NO \\
  \hline
  Themis~\cite{mengThemisDecentralizedEscrow2019} & \YES & \NO & \YES & \BC & \NO \\
  \hline
  Lelantos~\cite{altawyLelantosBlockchainBasedAnonymous2017} & \YES & \PSEUDO & \NO & \BC & \YES \\
  \hline
  This paper & \YES & \YES & \YES & \BC & \YES \\
  \hline

@@

The vision of smart contracts was to replace the legal contract with
programmable and autonomous contracts. The smart contract code encompasses the contract's specifications, hence the slogan \textit{code as a law}. Moreover, smart contracts are automatically executed merging together the gap of law and its enforcment by police~\cite{allenGovernanceBlockchainDispute2019}. However, the blockchain paradigm has its limitations.

Blockchain can assure the correctness of data existing only on the blockchain. The problem arises in the contact between blockchain and the real world, when we want the smart contract to decide based on some input from outside the blockchain. The technique of providing real-world data to the blockchain is called oracle. Oracle provides data based on a decentralized network of mediators; therefore, the trust is also decentralized~\cite{breidenbachChainlinkNextSteps2021}.

Some oracles provide the data like weather, soccer match result, stock
price, train delay, election results, others—and they are the ones we
are interested in—provide the settlement of a submitted dispute.

@@

Kleros~\cite{bergollaKlerosSociolegalCase2022} is a smart contract deployed on the Ethereum platform that mimics in a decentralized and autonomous way how the court works in real life. In Kleros, every process of a dispute like gathering evidence, selecting jurors, rewarding the winning party is automated by a set of smart contracts. Like Themis, the honesty of the agents voting in a case is achieved by game-theoretical economic incentives.

Such a decentralized, voluntary, and anonymous dispute resolution system might work for simple contracts violations like an eBay seller sending broken or wrong products or an Airbnb apartment being inadequate to the photos in the offer. However, it is hard to realize such decentralized evaluation of heath or legal services quality when expertise and privacy concerns are taken into account. Therefore, in our protocol, we take the more conservative approach and resolve disputes using local
justice system (police or court).

@@

Depending on a cryptocurrency, the link can be created in different
ways:
% continue reading from here
\begin{itemize}

>>>>

@@

Providing personal information exposes users to privacy risks, i.e. potential loss of control over personal information~\cite{smithInformationPrivacyResearch2011}.
%JS co może prowadzic do nieintencjonalnego naruszenia rodo  
%SP dodałem na dole

Such personal information can be used deliberately or accidently (e.g., by theft) 
%JS kradzież to chyba inencjonalne
%SB zmieniłem na accidentaly
for insider disclosure, unauthorized access, or commercial gains. For example, by reselling it to marketers, financial institutions, other businesses, government agencies, or even cybercriminals. 
In turn, it can lead to an unintentional violation of the GDPR or CCPA, profiled advertisements or even criminal activities like identity theft or illegal tracking and surveillance~\cite{smithInformationPrivacyResearch2011}.

Public individuals like influencers, politicians, or celebrities are especially vulnerable to this kind of attack as exposure of their health records, purchase habits, or legal documents can threaten their reputation, position or be used for blackmailing.

% SB START emphasise 
The problem amplifies when personal information is linked to biological materials like DNA, saliva, or blood, or legal documents like contracts, or wills.

In such situations, customers may be reluctant to provide their personal information to the SP and thus resign from the service. Both parties are harmed as the client does not receive a diagnosis relevant to their health and the SP loses potential clients. Both parties are affected as the client does not receive a diagnosis relevant to their health and the SP loses potential clients.
% SB END emphasise

The privacy guarantee of personal information is often based merely on trust assumptions and the security of the IT system. However, most SPs do not need the personal information for any other reason than payment or communication, which should be considered secondary compared to actual service provision.

It would be desirable for the user to keep his or her identity private while still receiving the service. This could lead to reduced trust that users have to put in SPs and less responsibility borne by SPs.

Examples of services that would benefit from the anonymity property are:
\begin{itemize}
    \item Patients willing to take a test eg.: for drugs, venereal diseases, paternity or steroids have a strong incentive to keep the whole procedure private. Merely the fact that they took the test—without exposing the result—is suggestive enough to act as a premise in case of a conflict.

Especially %celebrities, politicians, and %js powtorka
public figures are prone to this kind of problem as such precedent can negatively influence their future career.

Currently, they have to risk that their personal details, materials, and results are stored securely and kept private from any unauthorized actor (both curious employees and malicious attackers).

Our protocol allows taking such services anonymously, eliminating the strong trust assumption put on the service provider's (e.g., laboratory) IT system.
\item People willing to take risky business activities may be willing to receive the risk estimation and prediction of possible personal repercussions of such action.

By exposing our identity we trust that the lawyer will not use that information for harmful actions.

@@

%SB GOAL
In this work, we research the possibility of providing services without the collection of personal information.

@@

Our review of the state of the art indicates that none of the current systems is sufficient to achieve the desired goal. Therefore, we propose a protocol for anonymously provisioning services that require the delivery of physical materials. In case of dispute, either due to exceeding deadlines or providing an incorrect result, the customer can disclose the whole interaction and prove to justice the misbehavior of the SP.

To achieve these objectives, we use:
\begin{itemize}
    \item Blockchain (aka message board), to achieve fairness, i.e., as a means for proving that certain actions took place at a certain moment without the trusted third party (TTP).
    \item Anonymous payment methods, like cash or privacy-preserving cryptocurrencies, allow customers to pay for services anonymously.
    \item Content-addressable decentralized storage network (e.g., IPFS) to anonymously provide results to customers together with a provable storage network (e.g., Filecoin) to guarantee that the results are available to the customer even in case of the SP denial of service. 
    \item Cryptography
    \begin{itemize}
        \item Symmetric encryption, to encrypt and decrypt results published on the public networks.
        \item Public-key cryptography, and Diffie-Helman key exchange (DHKE) to derive shared secrets for symmetric encryption.
        \item Digital signatures, to achieve authentication and non-repudiation of actions. 
    \end{itemize}

@@

%\paragraph{Contributions}
%We contribute to the state of the art by:
The contribution of our paper is:
\begin{itemize}
\item proposing a novel protocol that:
  \begin{itemize}
  \item allows \textbf{anonymous} service provision, i.e., the service provider does not need to collect any personal information from the customer.
  \item achieves \textbf{fairness} by carefully designing the protocol as an interactive non-cooperative game, in which the SP remains in an advantageous position and the customer in a disadvantageous one with the option to start a dispute in case the SP misbehavior.
  \item \textbf{does not rely on centralized TTP}, but uses decentralized blockchain and distributed content-addressable storage network.
  \item abstracts the customers from the blockchain technology used underneath, allowing the use of our protocol for \textbf{non-technical users}.
  \item allows the \textbf{delivery of physical materials}, which was rarely addressed by other researchers or based on strong and unpractical assumptions.
  \item guarantees the \textbf{remote availability of the results}, even in case of the SP denial of service.
  \end{itemize} 
\item Systemise often misused definitions of anonymity, pseudonymity, linkability, and traceability.
\item Proposing a framework for analyzing fairness analysis in fair-exchange protocols.
\item Discuss the possible improvements to the protocol with the use of secure computation, self-sovereign identities, zero-knowledge proofs, and blockchain-based dispute resolution mechanisms.
\end{itemize}

@@

%\paragraph{Organisation}
The rest of this paper is organized as follows.
In section~\ref{sec:related-works} we review related works. 
Then, in section~\ref{sec:building-blocks} we discuss the building blocks of a dispute resolution system, blockchain as a message board, fairness, payment for services, storage network, result availability, anonymity, and confidentiality.
Section~\ref{sec:protocol} describes how the protocol works in detail.
Section~\ref{sec:fairness-analysis} provides a fairness analysis of the proposed protocol.
In Section~\ref{sec:experiments} we present the implementation of the protocol and results of our experiments.
Section~\ref{sec:discussion} discuss possible improvements in terms of crowd-sourced dispute resolution or dispute avoidance, self-sovereign identities (SSI), and anonymous delivery.
Finally, section~\ref{sec:conclusion} concludes the paper.

\section{Related Works}\label{sec:related-works}
In this section, we review related works on fair exchange, anonymous, and physical delivery protocols. Then we outline the main differences between our protocol and the existing ones.

\subsection{Fair exchange, physical delivery}
The most common application of fair exchange protocols is e-commerce. A typical transaction involves a seller and a buyer, who exchange money for a physical product such as a smartphone. To protect themselves, a seller would want to receive the funds prior to sending the product, while a buyer would want to receive the product prior to paying. The fairness of the protocol should guarantee that either both parties obtain the goods, or they both obtain nothing.

Authors of~\cite{mohammedalarajFairnessPhysicalProducts2012} proposed an protocol for fair-exchage involving physical materials delivery. The protocol assumes the existence of offline~\footnote{\textit{Offline} (also called \textit{optimistic}) TTP compared to \textit{online} TTP is in improvement which assumes the TTP being involved only in the case of a dispute between parties~\cite{rayFairExchangeEcommerce2002}.} TTP that is involved only in the case of a dispute. The protocol works as follows: 
\begin{enumerate}
\item The buyer sends an encrypted payment to the seller along with the proof of validity.
\item The seller validates the proof which convinces him that the decrypted payment will also be valid.
\item The seller forwards the physical product to the delivery agent.
\item The buyer verifies whether the product is the one he ordered.
\item The buyer creates a proof of delivery and sends it along with the decryption key to the seller.
\end{enumerate}

However, the protocol relies on strong assumptions, namely, the existence of a trusted third party (TTP) and trusted delivery agent which does not misbehave or collude with any party.

\begin{itemize}
    \item there exists a trusted third party (TTP) and trusted delivery agent which does not misbehave or collude with any party;
\end{itemize}

@@

In the previous protocol, the identities of both parties are known. There are however situations where the customer does not want to reveal his identity to the merchant. The problem gets even more challenging when physical products are involved.

Authors of~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} proposed a protocol for the fair exchange of physical products and electronic payments, which guarantees both customer and merchant anonymity. They achieve it by introducing online TTPs that validate coins and provide fair exchange guarantees.

The anonymity is ensured by assuming the existence of a source cabinet (SC), delivery cabinet (DC), and a trusted delivery agent who take a product from an SC and provide it to a DC.
Both cabinets provide access to the product by passwords to conceal
the identity of the customer and the merchant.

@@

\begin{enumerate}
    \item Both parties agree on the purchase details.
    \item The customer buys a digital coin from his bank and validates it with the TTP.
    \item The customer sends the merchant the purchase order and the digital signature made by TTP on the encrypted coin.
    \item The merchant post the product to the SC.
    \item Delivery agent collects the product from the SC and posts it to the DC.
    \item Customer collects the product from the DC using a password.
    \item The customer checks if the product is the ordered one.
    \begin{itemize}
    \item[-] if yes 
        \begin{enumerate}
        \setcounter{enumii}{7}
        \item the customer sends the acknowledgment to the DC and decryption key to the merchant.
        \item The merchant redeems the coins from the bank.
        \end{enumerate}
    \item[-] if no
        \begin{enumerate}
        \setcounter{enumii}{7}
        \item the DC is equipped with a video camera that records the moment when the customer opens the package and lets the customer signal the invalidity of the product, and so, sending the encrypted recording to the TTP. 
        \item the dispute is settled via TTP, optionally letting each party reveal its identity.
    \end{enumerate}
    \end{itemize}
\end{enumerate}
\endgroup

Besides the assumptions of the existence of TTP and trusted delivery agent (similar to the previous protocol~\cite{mohammedalarajFairnessPhysicalProducts2012}), the protocol also assumes:

\begin{itemize}
    \item there exists an anonymous communication channel 
    \item the customer's and merchant's banks enable confidential transactions, and both share a commit buffer where the value is locked until the transaction is finished;
    \item all banks maintain a global list of coins' serial numbers to prevent double-spending problems;
    \item the SC and DC exist, and in both, the access is protected by a password;
    \item the DC is equipped with a video camera that records the moment when the customer opens the package and provides a way to submit the video to TTP in case of a dispute;
\end{itemize}

@@

The issue of TTPs in fair exchange protocols has been solved by the usage of decentralized networks, especially blockchain technology.

The simplest example of blockchain-based fair exchange protocol is certified electronic mail protocol in which neither the sender can deny sending the mail, nor the receiver can deny receiving it. As the service is widely used in the paper world, achieving it for e-mails has not yet met agreement across the scientific community. The main problem was the dependency on TTP, which significantly reduced the performance, security, and robustness of such protocols. The protocols that do not use TTP struggle with high computation and communication overhead~\cite{hinarejosSolutionSecureCertified2019}.

@@

The idea behind certified e-mails and any other fair exchange protocols is the following:
\begin{enumerate}
    \item The sender sends an encrypted and signed message to the receiver.
    \item The receiver returns a proof of delivery (a signature) of the encrypted message to the sender.
    \item The sender publishes proof of delivery and the decryption key on a blockchain (or TTP in general).
    \item The receiver decrypts the encrypted message using the published decryption key.
\end{enumerate}

@@

Next, both Alice and Bob, take their key shares and encrypt each
\textit{i}-th key share using public key of \textit{i}-th mediator. As a result
Alice's secret \(x_A\) becomes \({c^A_1, c^A_2,...,c^A_n}\), and Bob's
secret \(x_B\) becomes \({c^B_1, c^B_2,...,c^B_n}\), where
\(c_i = E_{M_i}(P_i)\) is the encrypted \(i\)-th key share using
\(i\)-th mediator public key \(M_i\).

@@

In case of dispute, the decentralized network of mediators settles the conflict and grand one winning party, the other party secret key,
letting him withdraw the funds.

@@

A smart-contract is used to coordinate the whole process and
mediate communication between customers and delivery providers.

@@

Bîrjoveanu, 2015~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} is the closest to our protocol, however, it uses TTP and does not consider disputes between parties.

Hinarejos et al., 2019~\cite{hinarejosSolutionSecureCertified2019} is the simplest protocol that replaces TTP with blockchain. However, it does not consider anonymity, disputes between parties nor physical material exchange.

Meng et al., 2019~\cite{mengThemisDecentralizedEscrow2019} improves the previous protocol by the crowdsourced dispute resolution system. However, it does not take anonymity into consideration.

Altawy et al., 2017~\cite{altawyLelantosBlockchainBasedAnonymous2017} is a blockchain-based protocol that does not provide dispute resolution but provides anonymous physical delivery by using onion routing and anonymous blockchain interaction assuming unlinkability between pseudonyms and real identities.

The authors proposed many extensions to the protocol, namely, in ~\cite{birjoveanuPreservingAnonymityFair2018} they proposed a anonymous e-commerce protocol that govers complex transactions, in ~\cite{birjoveanuAnonymityComplexTransactions2019} they extend the anonimity for both customers and SPs, and in ~\cite{birjoveanuFairExchangeECommerce2020} they propose a protocol that supports chained transactions (involving multiple active intermediares). However none of them is relevant to our use case.

We want the SP to remain public so that the anonymous customer can easily start a dispute. We assume just one package of physical materials. Moreover, the package is delivered from the customer to the SP, not the other way around — as it's the case for most e-commerce transactions.

Our protocol achieves stronger anonymity guarantees. Namely, we achieve anonymity by using either cash or privacy-preserving blockchains. Moreover, our protocol does not require a customer to submit any transaction to the message board, which may be the weakest link in the anonymity of the aforementioned protocols.

Our protocol does not use its own delivery system. We assume that there is a way to anonymously deliver a package either via SP's drop box, a customer's trusted party. The improvement of the protocol to support anonymous physical delivery via courier is discussed in Section~\ref{sec:anonymous-delivery}.

Also, our protocol does not provide its own dispute-resolution mechanism as Themis does. However, we assume the existence of an abstract justice that accepts evidence and punishes the misbehaving party. 
%JS to warto podkreslic w dyskusji
It can be instantiated with either the local court or police, or one of the blockchain
dispute resolution services like Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros~\cite{bergollaKlerosSociolegalCase2022,gudkovCrowdArbitrationBlockchain2020}, Aragon Court\footnote{Aragon Court, Decentralized Dispute Resolution Protocol, https://aragon.org/aragon-court, (last visited Jan. 10, 2023)}, LTO Network\footnote{LTO Network, a hybrid blockchain application development platform for securing, verifying, and exchanging enterprise information, https://lto.network/, (last visited Jan. 17, 2023)}, and other Online Dispute Resolution platforms~\cite{allenGovernanceBlockchainDispute2019}.

The comparison of the protocols is presented in table~\ref{tab:comparision}.

\begin{table}
\newcommand{\YES}{\cellcolor{green!50}Yes}
\newcommand{\ID}{\cellcolor{green!25}Identity}
\newcommand{\PSEUDO}{\cellcolor{green!25}Pseudonym}
\newcommand{\ANON}{\cellcolor{green!50}Anonymity}
\newcommand{\NO}{\cellcolor{red!50}No}
\newcommand{\TTP}{\cellcolor{red!50}TTP}
\newcommand{\BC}{\cellcolor{green!50}BC}
\caption{Comparision of related works}
\label{tab:comparision}
\setlength{\tabcolsep}{3pt}

\ifx\JOURNAL\JOURNALIEEE
\begin{tabular}{|p{40pt}|p{35pt}|p{40pt}|p{35pt}|p{30pt}|p{30pt}|}
\else
\begin{tabular}{|c|c|c|c|c|c|}
\fi
\hline
Protocol & Fair exchange & Anonymity & Dispute resolution & Trust & Physical delivery \\
\hline
Alaraj, 2012~\cite{mohammedalarajFairnessPhysicalProducts2012} & \YES & \NO & \YES & \TTP & \YES \\
\hline
Bîrjoveanu, 2015~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} & \YES & \YES & \NO & \TTP & \YES \\
\hline
Hinarejos et al., 2019~\cite{hinarejosSolutionSecureCertified2019} & \YES & \NO & \NO & \BC & \NO \\
\hline
Themis~\cite{mengThemisDecentralizedEscrow2019} & \YES & \NO & \YES & \BC & \NO \\
\hline
Lelantos~\cite{altawyLelantosBlockchainBasedAnonymous2017} & \YES & \PSEUDO & \NO & \BC & \YES \\
\hline
This paper & \YES & \YES & \YES & \BC & \YES \\
\hline

@@

The vision of smart contracts was to replace the legal contract with
programmable and autonomous contracts. The smart contract code encompasses the contract's specifications, hence the slogan \textit{code as a law}. Moreover, smart contracts are automatically executed merging together the gap between law and its enforcement by police~\cite{allenGovernanceBlockchainDispute2019}. However, the blockchain paradigm has its limitations.

Blockchain can assure the correctness of data existing only on the blockchain. The problem arises in the contact between the blockchain and the real world when we want the smart contract to decide based on some input from outside the blockchain. The technique of providing real-world data to the blockchain is called an oracle. Oracle provides data based on a decentralized network of mediators; therefore, the trust is also decentralized~\cite{breidenbachChainlinkNextSteps2021}.

Some oracles provide the data like weather, soccer match result, stock
price, train delay, election results, and others—and they are the ones we
are interested in—providing the settlement of a submitted dispute.

@@

Kleros~\cite{bergollaKlerosSociolegalCase2022} is a smart contract deployed on the Ethereum platform that mimics in a decentralized and autonomous way how the court works in real life. In Kleros, every process of a dispute like gathering evidence, selecting jurors, and rewarding the winning party is automated by a set of smart contracts. Like Themis, the honesty of the agents voting in a case is achieved by game-theoretical economic incentives.

Such a decentralized, voluntary, and anonymous dispute resolution system might work for simple contracts violations like an eBay seller sending broken or wrong products or an Airbnb apartment being inadequate to the photos in the offer. However, it is hard to realize such a decentralized evaluation of health or legal services quality when expertise and privacy concerns are taken into account. Therefore, in our protocol, we take the more conservative approach and resolve disputes using local
justice system (police or court).

@@

Depending on the cryptocurrency, the link can be created in different
ways:
% continue reading from here
\begin{itemize}
